---
title: "Report for June 29th Data"
author: "Adam Levin"

output: html_document
---

```{r, echo=FALSE, message=FALSE,  include=FALSE}
#necessary libraries and data
library(dplyr)
library(tidyr)
library(ggplot2)
fluxes = readr::read_csv("fluxes.csv")
collar_map = readr::read_csv("collar_map.csv")

#theme for document 
theme_set(theme_classic())
```

# **Influence of Biotic Interactions on Resiliance to Storm Conditions**

### **Dataset Overview**   
The data set corresponds to the experiement outlined     in _"Do biotic interactions control coastal forest resilience to extreme storm events?"_

### **Relevant Points**
```{R, echo = FALSE}
#cean up both datasets
fluxesTidy = 
  (fluxes %>% 
    gather(date, value, 2:7))
collarMapTidy = 
  collar_map %>% select(-LI8100A_Port, -Group, -Plot)
#merge the datasets pre filter data to find total observations
collarInfoPreFilter =
  collarMapTidy %>% left_join(fluxesTidy, "Collar")
#general collarInfo
collarInfo = collarInfoPreFilter %>%
  filter(!is.na(value))


```

Number of Observations = **`r collarInfoPreFilter %>% summarize(n()) `**

Minimum Flux = **`r collarInfo$value %>% min()`**

Maximum Flux = **`r collarInfo$value %>% max()`**

```{r, echo = FALSE}
#set up for date info (final and first)
sortedByDate = collarInfo$date %>% sort(decreasing = FALSE) #sort collar info sorted by date 
```

First Date = **`r sortedByDate[1]`**

Final Date = **`r sortedByDate %>% last()`**

### **Dataset Summary by Treatment**
```{r, echo = FALSE}
infoByTreatment = collarInfo %>% group_by(Treatment) %>% summarize(mean(value), sd(value), n()) 
print(infoByTreatment)
```


```{r, echo = FALSE, message=FALSE}
#setup for means and stdev by treatment and date
statsByBoth = collarInfo %>% group_by(date, Treatment) %>% summarize(means = mean(value), stDevds = sd(value))

#setup for graphs
boxplotGraph = collarInfo %>% ggplot(aes(value, Treatment)) + geom_boxplot() + geom_jitter(height = 0) + ggtitle("Boxplots of Flux by Treatment")

lineMeanBothGraph = statsByBoth %>% ggplot(aes(date, means, group = Treatment, color = Treatment)) + geom_line() + ggtitle("Mean Flux by Date and Treatment") + xlab("Date") + ylab("Mean Flux")
```

### **Relevant Graphs**
```{r, echo = FALSE}
boxplotGraph

lineMeanBothGraph
```

### **Information on Collars not Included**
```{r, echo=FALSE} 
collarsNotIncluded = collarInfoPreFilter %>% filter(is.na(value)) %>% select(-value)
collarsNotIncluded
```

`r c(0, 2)`

### **Ending Session Info**
```{r, echo = FALSE}
sessionInfo()
```
