---
title: "Report for June 29th Data"
author: "Adam Levin"

output: html_document
---

```{r, echo=FALSE, message=FALSE,  include=FALSE}
#necessary libraries and data
library(dplyr)
library(tidyr)
fluxes = readr::read_csv("fluxes.csv")
collar_map = readr::read_csv("collar_map.csv")
```

# **Influence of Biotic Interactions on Resiliance to Storm Conditions**

### **Dataset Overview**   
The data set corresponds to the experiement outlined in _"Do biotic interactions control coastal forest resilience to extreme storm events?"_

### **Relevant Points**
```{R, echo = FALSE}
#shape into a single dataset with relevant columns
fluxesTidy = 
  (fluxes %>% 
    gather(date, value, 2:7))
collarMapTidy = 
  collar_map %>% select(-LI8100A_Port, -Group, -Plot)
#pre filter data to find total observations
collarInfoPreFilter =
  collarMapTidy %>% left_join(fluxesTidy, "Collar")
#general collarInfo
collarInfo = collarInfoPreFilter %>%
  filter(!is.na(value))
  
sortedByDate = collarInfo$date %>% sort(decreasing = FALSE) #sort collar info sorted by date 

```

Number of Observations = **`r collarInfoPreFilter %>% dplyr::summarize(n()) `**

Minimum Flux = **`r collarInfo[4] %>% min()`**

Maximum Flux = **`r collarInfo[4] %>% max()`**

First Date = **`r sortedByDate[1]`**

Final Date = **`r sortedByDate %>% last()`**

### **Ending Session Info**
```{r, echo = FALSE}
sessionInfo()
```
